Learning and comparing functional connectomes across subjects

### 2013-01-01 paper.tex
iter

\begin{abstract}
    Functional connectomes capture brain interactions via 
    fluctuations in brain imaging signal. On rest data they map
    the intrinsic functional architecture of the brain and with
    task-driven experiments they represent the integration mechanisms
    between specialized brain areas. Analysis of their variability 
    across subjects and conditions can reveal markers of brain
    pathologies and cognitive mechanisms. However, connectomes are
    complex multivariate objects. Methods to estimate them 
    from the functional signal have undergone rapid developments.
    The literature is full of diverse strategies to compare them.
    This paper aims to clarify some links across functional-connectivity
    methods and expose different steps to perform a group study on
    functional connectomes.
\end{abstract}

>>>>

\begin{abstract}
    Functional connectomes capture brain interactions via 
    fluctuations in brain imaging signal. On rest data they map
    the intrinsic functional architecture of the brain. With
    task-driven experiments they represent the integration mechanisms
    between specialized brain areas. Analysis of their variability 
    across subjects and conditions can reveal markers of brain
    pathologies and cognitive mechanisms. However, connectomes are
    complex multivariate objects. Methods to estimate them 
    from the functional signal have undergone rapid developments.
    The literature is full of diverse strategies to compare them.
    This paper aims to clarify some links across functional-connectivity
    methods and expose different steps to perform a group study on
    functional connectomes.
\end{abstract}
